Bricking up backdoors in Intrusion Detection Systems

### 2019-09-16 paper/pruning_example.tex

\begin{adjustbox}{valign=t}
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=0, my depth label=3, \goodNodeStyle]
        ]   
            [x_1 \leq 1.6,
              [0, edge+=dashed, name=leafLegend, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4]
            ]   
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 1}};
%
    \node[align=center, below = \legendspace of leafLegend] (leafLabel) {0=\protect\sethlcolor{green}\hl{benign}, 1=attack\\ dashed line: leaf that is going to be cut};
    \draw[->] (leafLabel) -- (leafLegend);
\end{forest}
\end{adjustbox}

>>>>

\begin{adjustbox}{valign=t}
\begin{forest}    
    [x_2 \leq 3.1, name=top
        [x_1 \leq -2, name=l2l
            [1, tier=3, my usages label=10, my depth label=3] 
            [0, tier=3, my usages label=0, my depth label=3, \goodNodeStyle]
        ]   
            [x_1 \leq 1.6,
              [0, edge+=dashed, name=leafLegend, my usages label=0, my depth label=4, \goodNodeStyle] 
              [1, my usages label=1, my depth label=4]
            ]   
        ]   
    ]
    \node[above=\topspace ,align=center,anchor=center] {\textsf{Step 1}};
%
    \node[align=center, below = \legendspace of leafLegend] (leafLabel) {\protect\sethlcolor{green}\hl{0=benign}, 1=attack\\ dashed line: leaf that is going to be cut};
    \draw[->] (leafLabel) -- (leafLegend);
\end{forest}
\end{adjustbox}
